The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables

### 2015-01-18 draft.tex
Some more edits- pushing for laptop

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color} 
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{subfigure}
%\usepackage{epsfig}
%\usepackage[dvips]{color}
%\usepackage{aabib}

@@

\py is a Monte Carlo  ionization and radiative transfer code which
uses the Sobolev approximation to treat line transfer. It has already
been described extensively in LK02, SDL05 and H13, so here we provide
only a brief summary of its operation, focusing particularly on new
aspects of our implementation of macro-atoms into the code.

@@

We generally use the same atomic data as H13, which is an updated
version of that described in LK02. In addition, we follow SDL05 in
treating Hydrogen as a 20-level atom, where each level is defined by
the principal quantum number, $n$. For the macro-atom treatment of
Helium,  we have added additional level and line information required 
from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{II} is treated
in much the same way as H, but with 10 levels. He~\textsc{I} has
larger energy differentials between different l-subshells and triplet
and singlet states. Thus, we still include levels up to $n=10$ but
explicitly treat the $l$ and $s$ sub-orbitals as distinct levels
instead of assuming they are perfectly `l-mixed'. This allows us
to model the singlet and  triplet He~\textsc{i} lines that are ubiquitous
in the optical spectra of CVs \citep[e.g.][]{dhillon1996}.

@@

\py includes several different kinematic models of accretion disk
winds, as well as different options for describing the physical and
radiative properties of the wind-driving system under
consideration. Most of these features have already been discussed in
LK02 and H13, so below we only briefly recount the key aspects of the
particular system and wind model used in the present study.

@@

The ionization equation used in the ``simple atom'' approach used in
LK02 (see section~\ref{simpleatoms}) should be a reasonable approximation to
the photoionization equilibrium in the benchmark wind model. Even
though the macro-atom treatment of H and He does affect the 
computation of the overall ionization equilibrium, we would expect the
resulting ionization state of the wind to be quite similar to that
found in LK02. The bottom panels in figure~\ref{wind} confirm that this
is the case. In particular, Helium is fully ionized
throughout most of the outflow, except for a small region near the
base of the wind, which is shielded from the photons produced by the
hot inner disk. In line with the results shown in LK02, we also find
that C\textsc{iv} is the dominant Carbon ion throughout the wind,
resulting in a substantial absorbing column across a large range of
velocities. As we shall see, this produces the broad, deep and
blue-shifted C\textsc{iv}~$\lambda 1550{\rm \AA}$ absorption line that
is usually the most prominent wind-formed feature in the UV spectra of
low-inclination nova-like CVs.

@@

We begin by verifying that the benchmark model still produces UV
spectra that resemble those observed in CVs. We do expect this to be
the case, since the ionization state of the wind has not changed
significantly from that computed in LK02 (see section~\ref{modela_ionization}). 
The left column of panels in figure~\ref{spec} shows that this expectation
is met: all of the strong metal resonance
lines - notably N\textsc{v}~$\lambda 1240{\rm \AA}$,
Si\textsc{iv}~$\lambda 1400{\rm \AA}$ and C\textsc{iv}~$\lambda
1550{\rm \AA}$ - are present and exhibit clear P-Cygni profiles
at intermediate inclinations. In addition, however, we now also find
that the wind produces significant Lyman-$\alpha$ and
He~\textsc{ii}~$\lambda1640{\rm \AA}$ emission lines.

@@

Figure~\ref{spec} shows the corresponding optical spectra produced for
the benchmark model, and these do exhibit some emission lines
associated with H and He. 
We see a general trend from absorption lines to emission lines 
with increasing inclination, as one might expect from our wind
geometry. This trend is consistent with observations, as can be  seen
in Figure~1. However, it is clear that this particular model
does not produce all the lines seen in observations of high-state CVs.
The higher order Balmer series lines are too weak
to overcome the intrinsic absorption from the disk atmosphere, and the wind 
fails to produce any emission at intermediate inclinations, 
which contrasts with (for example) the observed behaviour of IX Vel
\citep{beuermann1990}.

The emissivity of these recombination 
features scales as $\rho^2$, meaning that they form almost entirely in the 
dense base of the wind, just above the accretion disk. Here, the
velocity field of the wind is still dominated by rotation, rather than
outflow, which accounts for the double-peaked shape of the lines. In
principle, lines formed in this region can still be single peaked,
since the existence of a poloidal velocity {\em gradient} changes the
local escape probabilities (MC96). However, as
discussed further in section~\ref{modelb}, the 
radial velocity shear in our
models is not high enough for this radiative transfer effect
to dominate the line shapes.

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/modelb_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, 
while the green line shows disk photons which escape without being reprocessed by
the wind. The red line show the contributions from reprocessed 
photons. 
In this denser model the reprocessed contribution is significant compared
to the escaping disk spectrum. The Balmer continuum emission is prominent, and
we can see a clear effect on the overall spectral shape from the wind.}
\label{modelb_escape}
\end{figure}

@@

Our models do not exhibit P-Cygni profiles in the optical lines.
This is perhaps not surprising. LK02 and SV93 originally designed such models
to reproduce the UV line profiles. Thus, most of the wind
has an ionization parameter of $\log U \sim 2$ (see figure 6).
This means Hydrogen and Helium are fully ionized throughout 
much of the wind and is successful in producing recombination features.
However, it leads to absorbing columns in H of $N_H\sim ??$ - far too
low to produce noticeable blue shifted absorption. 
We therefore suspect that the winds that exhibit such profiles must 
possess a higher degree of ionization stratification.
This could manifest as a clumpy flow, in which ionization changes
due to small scale density fluctuations, or a stratification on acceleration 
length scales such as the kind shown by figure 6.
This idea is supported by the fact that \cite{prinja2000}
found dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
by observing the UV resonance lines in outburst with the {\sl Hubble Space Telescope}.
This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876{\rm \AA}$
and \ha\ when in a high-state \cite{patterson1996,RN98}.

@@

The wind now also has a clear effect on the continuum shape,
as shown by figure~\ref{modelb_escape}. The majority of the
escaping spectrum has now been reprocessed in some way by the wind,
either by electron scattering (the wind is now moderately Thompson-thick),
or by bound-free processes. This is demonstrated by the flatter spectral shape
and the slight Helum photoabsorption edges present in the optical spectrum.
In addition, figures~11 and 12 clearly demonstrate that the wind produces
a recombination continuum sufficient to completely fill in the Balmer jump
at high inclinations.\footnote{Note that the apparent absorption feature 
just redward of the Balmer jump in these models is artificial. It is
caused by residual line blanketing in the stellar atmospheres, which
our models cannot fill in since they employ a 20-level Hydrogen atom.}
This offers a potential solution to a long-standing problem in
understanding the spectral energy distribution of CVs, as
originally suggested by \cite{KLWB98}.

@@

Figure~\ref{halpha} shows how the H$\alpha$
line changes with the kinematics of the wind
for an inclination of $80^\circ$. 
The line narrows as the models move towards denser,
more slowly accelerating winds. 
This is due
the base of the wind becoming optically thick such 
that line emission cannot escape. This means
what is effectively a photosphere for the line moves 
to a greater vertical distance from the disk plane,
where rotational velocities drop off as $1/r$. 
The narrowing of the line is {\em not} due to the radial velocity shear
mechanism proposed by MC96.
The main criterion for this mechanism is

\begin{equation}
\frac{dv_p}{dr} > \frac{dv_\phi}{ds}\,
\end{equation}

where $v_p$ is the poloidal velocity and $v_\phi$
is the Keplerian velocity.
This criterion is simply not satisfied in the emission region of our models.

There are two possible ways in which the model
could be altered to better reproduce single-peaked
lines as a result of radial velocity shear. First,
one could adopt a more equatorial wind geometry. 
This would increase the velocity gradient in the radial 
direction. However, CV winds are known to be moderately collimated.
This is demonstrated by the fact that blue-shifted resonance line 
absorption is seen in low inclination systems such as RW Sex \citep{greensteinoke1982},
but not in eclipsing systems \citep{cordovamason1985}.
Furthermore, the main reason for adopting this type of 
wind geometry is that it already successfully models the 
P-Cygni resonance lines seen in the UV (LK02; Noebauer et al. 2010),
Equatorial winds are expected in AGN and X-ray binaries 
\citep{weymann1991, ponti2012}, so these winds may be more likely
to possess the required kinematics.
Second, one could adopt velocity laws with higher 
velocity gradients in the line emission region. 
However, this poses problems for a smooth biconical wind. 
We have already demonstrated that high densities are required 
to produce significant emission. In a smooth model, which
satisfies the mass continuity condition (see section 3.1), 
it is therefore difficult to reconcile 
these high densities with the high velocity gradients required.

We suggest that clumping
in CV winds provides a possible solution.
Inhomogeneity could allow higher density pockets 
of emission to exist while still possessing a high radial velocity shear.
Theory of line-driven winds predicts an unstable flow
\citep{macgregor1979,owockirybicki1984,owockirybicki1985},
and simulations of accretion disk winds find a nonhomogeneous 
density structure \citep{proga1998,pkdh2002}.
In addition, a number of implementations have been used in the stellar wind
community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}. 
We therefore hope that further investigation of
`clumpy' winds could help solve the current mystery of single-peaked 
line emission in high inclination systems.

@@

Figure~\ref{rwtricomp} shows a qualitative comparison of the predicted
out-of-eclipse and mid-eclipse spectra against observations of the
high-inclination nova-like RW~Tri. The inclination of RW Tri is
somewhat uncertain, with estimates including $70.5^\circ$
\citep{smak1995}, $75^\circ$ \citep{groot2004}, $80^\circ$
\citep{longmore1981} and $82^\circ$\citep{frankking1981}. Here, we
adopt $i = 80^\circ$, but our qualitative conclusions are not
particular sensitive to this particular value. We emphasize that this
model is in no sense a fit to this - or any other - data set.

@@

There are also interesting differences between the revised
model and the RW Tri data set. For example, the model exhibits
considerably stronger He~{\sc ii} features than the observations,
which suggests that the overall ionization state of the model is
somewhat too high. 
As discussed in section 5.3, the optical lines are
narrow. This is in contrast to what is generally seen in observations
of NLs, although the relatively low resolution of the RW Tri
spectra makes a specific comparison difficult.

@@

Although we note that limb darkening effects on disk atmosphere opacities
would affect the Balmer jump (see section 5.2). In section 5.3, we demonstrate that
although single-peaked emission can be formed in our densest models, 
it is not due to the radial velocity shear mechanism proposed by MC96.
The emission in our models which produce single-peaked lines comes from
approximately $10^{11}$~cm above the disk plane, which is not supported
by eclipse-mapping observations (REFS). We suggest
that nonhomogenous, `clumpy' line-driven winds may offer a potential solution.

@@

\noindent We can also make a number of basic,
testable predictions for wind-formed signatures:
\begin{itemize}
	\item we expect the depth of the Balmer absorption edge in CV
          spectra to decrease with increasing inclination (with the
          Balmer jump possibly switching to emission at the highest
          inclinations, if the flux in the wind-formed recombination
          continuum exceeds that of the foreshortened disk spectrum);
	\item we predict that a strong He~\textsc{ii}~$\lambda3202{\rm
          \AA}$ line should be prominent in all cases where
          He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& \heiiopt\ are seen
          (but note that this prediction is not restricted to lines
          formed in disk winds);
	\item we predict that the Balmer jump should be in emission
          during mid-eclipse in high inclination systems.
\end{itemize}

>>>>

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color} 
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{aastex}
%\usepackage{epsfig}
%\usepackage[dvips]{color}
%\usepackage{aabib}

@@

\py is a Monte Carlo  ionization and radiative transfer code which
uses the Sobolev approximation to treat line transfer. It has already
been described extensively by LK02, SDL05 and H13, so here we provide
only a brief summary of its operation, focusing particularly on new
aspects of our implementation of macro-atoms into the code.

@@

We generally use the same atomic data as H13, which is an updated
version of that described by LK02. In addition, we follow SDL05 in
treating Hydrogen as a 20-level atom, where each level is defined by
the principal quantum number, $n$. For the macro-atom treatment of
Helium,  we have added additional level and line information required 
from \textsc{Topbase} \citep{topbase2005}.  He~\textsc{II} is treated
in much the same way as H, but with 10 levels. He~\textsc{I} has
larger energy differentials between different l-subshells and triplet
and singlet states. Thus, we still include levels up to $n=10$ but
explicitly treat the $l$ and $s$ sub-orbitals as distinct levels
instead of assuming they are perfectly `l-mixed'. This allows us
to model the singlet and  triplet He~\textsc{i} lines that are ubiquitous
in the optical spectra of CVs \citep[e.g.][]{dhillon1996}.

@@

\py includes several different kinematic models of accretion disk
winds, as well as different options for describing the physical and
radiative properties of the wind-driving system under
consideration. Most of these features have already been discussed by
LK02 and H13, so below we only briefly recount the key aspects of the
particular system and wind model used in the present study.

@@

The ionization equation used in the ``simple atom'' approach used by
LK02 (see section~\ref{simpleatoms}) should be a reasonable approximation to
the photoionization equilibrium in the benchmark wind model. Even
though the macro-atom treatment of H and He does affect the 
computation of the overall ionization equilibrium, we would expect the
resulting ionization state of the wind to be quite similar to that
found by LK02. The bottom panels in figure~\ref{wind} confirm that this
is the case. In particular, Helium is fully ionized
throughout most of the outflow, except for a small region near the
base of the wind, which is shielded from the photons produced by the
hot inner disk. In line with the results of LK02, we also find
that C\textsc{iv} is the dominant Carbon ion throughout the wind,
resulting in a substantial absorbing column across a large range of
velocities. As we shall see, this produces the broad, deep and
blue-shifted C\textsc{iv}~$\lambda 1550{\rm \AA}$ absorption line that
is usually the most prominent wind-formed feature in the UV spectra of
low-inclination nova-like CVs.

@@

We begin by verifying that the benchmark model still produces UV
spectra that resemble those observed in CVs. We do expect this to be
the case, since the ionization state of the wind has not changed
significantly from that computed by LK02 (see section~\ref{modela_ionization}). 
The left column of panels in figure~\ref{spec} shows that this expectation
is met: all of the strong metal resonance
lines - notably N\textsc{v}~$\lambda 1240{\rm \AA}$,
Si\textsc{iv}~$\lambda 1400{\rm \AA}$ and C\textsc{iv}~$\lambda
1550{\rm \AA}$ - are present and exhibit clear P-Cygni profiles
at intermediate inclinations. In addition, however, we now also find
that the wind produces significant Lyman-$\alpha$ and
He~\textsc{ii}~$\lambda1640{\rm \AA}$ emission lines.

@@

Figure~\ref{spec} shows the corresponding optical spectra produced for
the benchmark model, and these do exhibit some emission lines
associated with H and He. 
We see a general trend from absorption lines to emission lines 
with increasing inclination, as one might expect from our wind
geometry. This trend is consistent with observations, as can be  seen
in Figure~1. However, it is clear that this particular model
does not produce all the lines seen in observations of high-state CVs.
The higher order Balmer series lines are too weak
to overcome the intrinsic absorption from the disk atmosphere, and the wind 
fails to produce any emission at intermediate inclinations, 
which contrasts with (for example) the observed behaviour of V3885 Sgr \citep{hartley2005}
and IX Vel \citep[][see also figure 1]{beuermann1990}.

The emissivity of these recombination 
features scales as $\rho^2$, meaning that they form almost entirely in the 
dense base of the wind, just above the accretion disk. Here, the
velocity field of the wind is still dominated by rotation, rather than
outflow, which accounts for the double-peaked shape of the lines. In
principle, lines formed in this region can still be single peaked,
since the existence of a poloidal velocity {\em gradient} changes the
local escape probabilities (MC96). However, as
discussed further in section~5.3, the 
radial velocity shear in our
models is not high enough for this radiative transfer effect
to dominate the line shapes.

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/modelb_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, 
while the green line shows disk photons which escape without being reprocessed by
the wind. The red line show the contributions from reprocessed 
photons. 
In this denser model the reprocessed contribution is significant compared
to the escaping disk spectrum. The Balmer continuum emission is prominent, and
the wind has a clear effect on the overall spectral shape.}
\label{modelb_escape}
\end{figure}

@@

Our models do not exhibit P-Cygni profiles in the optical lines.
This is perhaps not surprising. LK02 and SV93 originally designed such models
to reproduce the UV line profiles. Thus, most of the wind
has an ionization parameter of $\log U \sim 2$ (see figure 6).
This means Hydrogen and Helium are fully ionized throughout 
much of the wind and is successful in producing recombination features.
However, the line opacity throughout the wind it too
low to produce noticeable blue shifted absorption. 
We suspect that the winds that exhibit such profiles must 
possess a higher degree of ionization stratification, although the lack 
of contemporary observations means it is not known for certain if the 
P-Cygni profiles in UV resonance lines and optical H and He lines exist simultaneously.
Ionization stratification could manifest as a clumpy flow, in which ionization changes
due to small scale density fluctuations, or a stratification in density
and ionizing radiation field over larger scales.
Tentative evidence for clumping comes from the fact that \cite{prinja2000}
found dwarf nova BZ Cam's outflow to be unsteady and highly mass-loaded in outburst,
by observing the UV resonance lines.
This system has exhibited P-Cygni profiles in He~\textsc{i}~$\lambda5876{\rm \AA}$
and \ha\ when in a high-state \cite{patterson1996,RN98}. 
We also note that the degree of ionization and density variation and 
subsequent line opacities may be affected by our model parameters
and the specific parameterisation adopted.

@@

The wind now also has a clear effect on the continuum shape,
as shown by figure~\ref{modelb_escape}. The majority of the
escaping spectrum has now been reprocessed in some way by the wind,
either by electron scattering (the wind is now moderately Thompson-thick),
or by bound-free processes. This is demonstrated by the flatter spectral shape
and the slight Helium photoabsorption edges present in the optical spectrum.
In addition, figures~11 and 12 clearly demonstrate that the wind produces
a recombination continuum sufficient to completely fill in the Balmer jump
at high inclinations.\footnote{Note that the apparent absorption feature 
just redward of the Balmer jump in these models is artificial. It is
caused by residual line blanketing in the stellar atmospheres, which
our models cannot fill in since they employ a 20-level Hydrogen atom.}
This offers a potential solution to a long-standing problem in
understanding the spectral energy distribution of CVs, as
originally suggested by \cite{KLWB98}.

@@

Figure~13 shows how the H$\alpha$
line changes with the kinematics of the wind
for an inclination of $80^\circ$. 
The line narrows as the models move towards denser,
more slowly accelerating winds. 
This is due the base of the wind becoming optically thick such 
that line emission cannot escape. This means
what is effectively a photosphere for the line moves 
to a greater vertical distance from the disk plane,
where rotational velocities drop off as $1/r$. 
The narrowing of the line is {\em not} due to the radial velocity shear
mechanism proposed by MC96.
The main criterion for this mechanism to work is that

\begin{equation}
\frac{dv_p}{dr} \gtrsim \frac{dv_\phi}{dr},
\end{equation}

where $v_p$ is the poloidal velocity and $v_\phi$
is the Keplerian velocity. This criterion is simply 
not satisfied in the emission region of our models.
MC96 find values of $2-6.5$ for the ratio $(dv_p/dr)/(dv_\phi/dr)$
in their simple model, but in even our fastest accelerating 
wind we find ratios of $\lesssim0.1$ in the main \ha\ emission region.
The relatively low poloidal gradients are required to produce high densities
and observable emission lines, although 
we stress that the velocity field may depend significantly 
on the particular parameterisation used. 
We also suggest investigating clumping in CV winds.
Inhomogeneity could allow higher density pockets 
of emission to exist while still possessing a high radial velocity shear.
Theory of line-driven winds predicts an unstable flow
\citep{macgregor1979,owockirybicki1984,owockirybicki1985},
and simulations of accretion disk winds find a nonhomogeneous 
density structure \citep{proga1998,pkdh2002}.
In addition, a number of implementations have been used in the stellar wind
community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}.

The emission in our models which produce single-peaked lines comes from
approximately $10^{11}$~cm ($\sim150~R_{WD}$) above the disk plane.
Most models for Balmer emission in CVs propose that the Balmer emission
is more or less confined to the disk plane (e.g, MC96; REFs), 
and one might naively expect that the size of the emission region
is comparable to the size of the accretion disk, i.e., 10s-100s of WD radii.
However, the true vertical extent of the emission region is not known,
and it has been shown in multiple observations of eclipsing NLs that the 
H$\alpha$ line is only moderately eclipsed compared to the continuum 
(REFs, see also section 5.4).
We do not necessarily proposed that the emitting region is this large,
but it is a natural avenue to explore and a simple way in which to form
single-peaked lines.

% Alternatively, there are possible ways in which the model
% could be altered to better reproduce single-peaked
% lines as a result of radial velocity shear. First,
% one could adopt a more equatorial wind geometry. 
% This would increase the velocity gradient in the radial 
% direction. However, CV winds are known to be moderately collimated.
% This is demonstrated by the fact that blue-shifted resonance line 
% absorption is seen in low inclination systems such as RW Sex \citep{greensteinoke1982},
% but not in eclipsing systems \citep{cordovamason1985}.
% Furthermore, the main reason for adopting this type of 
% wind geometry is that it already successfully models the 
% P-Cygni resonance lines seen in the UV (LK02; Noebauer et al. 2010),
% Equatorial winds are expected in AGN and X-ray binaries 
% \citep{weymann1991, ponti2012}, so these winds may be more likely
% to possess the required kinematics.
% Second, one could adopt velocity laws with higher 
% velocity gradients in the line emission region. 
% However, this poses problems for a smooth biconical wind. 
% We have already demonstrated that high densities are required 
% to produce significant emission. In a smooth model, which
% satisfies the mass continuity condition (see section 3.1), 
% it is therefore difficult to reconcile 
% these high densities with the high velocity gradients required.

% We suggest that clumping
% in CV winds provides a possible solution.
% Inhomogeneity could allow higher density pockets 
% of emission to exist while still possessing a high radial velocity shear.
% Theory of line-driven winds predicts an unstable flow
% \citep{macgregor1979,owockirybicki1984,owockirybicki1985},
% and simulations of accretion disk winds find a nonhomogeneous 
% density structure \citep{proga1998,pkdh2002}.
% In addition, a number of implementations have been used in the stellar wind
% community \citep[e.g.][]{hamannkoesterke1998,oskinova2007}. 
% We therefore hope that further investigation of
% clumpy winds could help shed light on the formation of single-peaked 
% line emission in high inclination systems.
% It should be stressed again that these conclusions may, as mentioned in 
% section 5.1, be dependent on our particular parameterisation.
% By way of example, specific assumptions about the initial and 
% terminal velocities may significantly affect velocity gradients
% in regions dominated by rotational velocities.

@@

Figure~\ref{rwtricomp} shows a qualitative comparison of the predicted
out-of-eclipse and mid-eclipse spectra against observations of the
high-inclination nova-like RW~Tri. The inclination of RW Tri is
somewhat uncertain, with estimates including $70.5^\circ$
\citep{smak1995}, $75^\circ$ \citep{groot2004}, $80^\circ$
\citep{longmore1981} and $82^\circ$\citep{frankking1981}. Here, we
adopt $i = 80^\circ$, but our qualitative conclusions are not
particularly sensitive to this value. We emphasize that this
model is in no sense a fit to this - or any other - data set.

@@

There are also interesting differences between the revised
model and the RW Tri data set. For example, the model exhibits
considerably stronger He~{\sc ii} features than the observations,
which suggests that the overall ionization state of the model is
somewhat too high. 
As discussed in section 5.3, the optical lines are
narrow, but double-peaked. 
This is in contrast to what is generally seen in observations
of NLs, although the relatively low resolution of the RW Tri
spectrum makes a specific comparison difficult.

@@

Although we note that limb darkening effects on disk atmosphere opacities
would affect the Balmer jump (see section 5.2). In section 5.3, we demonstrate that
although the double peaked lines narrow 
single-peaked emission can be formed in our densest models, 
it is not due to the radial velocity shear mechanism proposed by MC96.
We suggest that nonhomogenous, `clumpy' line-driven winds may offer a 
potential solution.

@@

We can also make a number of basic,
testable predictions for wind-formed signatures:
\begin{itemize}
	\item we expect the depth of the Balmer absorption edge in CV
          spectra to decrease with increasing inclination (with the
          Balmer jump possibly switching to emission at the highest
          inclinations, if the flux in the wind-formed recombination
          continuum exceeds that of the foreshortened disk spectrum);
	\item we predict that a strong He~\textsc{ii}~$\lambda3202{\rm
          \AA}$ line should be prominent in all cases where
          He~\textsc{ii}~$\lambda1640{\rm \AA}$ \& \heiiopt\ are seen
          (but note that this prediction is not restricted to lines
          formed in disk winds);
	\item we predict that the Balmer jump should be in emission
          during mid-eclipse in high inclination systems.
\end{itemize}
